---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  geno: "no data"
  factor: "no data"
  data: "no data"
  maxp: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---
  
  ```{r, echo = FALSE}
library(knitr)

traits <- params$traits
geno <- params$geno
factor <- params$factor
data <- params$data
maxp <- params$maxp

data[, geno] <- as.character(data[, geno])
data[, factor] <- as.factor(data[,factor]) 
```

# 1. Linear Discriminant Analysis

The Linear Discriminant Analysis (`LDA`) is a dimensionality reduction techinique based on supervised learning or classification. This technique consist on finding a linear combination of features which characterizes or separates two or more classes of objects or events. The resulting combination may be used as a linear classifier, or, more commonly, for dimensionality reduction before later classification.

The components of the model are:

* X: a quantitative variable(s) that represent an attribute, feature or predictor.
* Y: a cualitative variable which has the set of classes or labels.
* Find a a good predictor function $f$ for the class $Y$ of any sample of the same distribution given only an observation of $X$. It is represent by:

$$
    f:X{\rightarrow}Y 
$$
Where 
 
* $X = \left(x_{ij})\right$ that represent the ${ith}$ observation of the $jth$ attribute or predictor. 
* $Y = \left(y_{j})\right$ that represent the {jth} class or label.




# 2. Model evaluation and Selection

```{r, echo = FALSE}
model_data <- na.omit(data) #Omitir NAs#
set.seed(1)
intrain <- sample(nrow(model_data), round(0.50*nrow(model_data)))
train <- model_data[intrain, ]
test <- model_data[-intrain, ]
library(MASS)
#5.3. Calcular el valor de prediccion de tramamiento con un grupo de variables a elegir 
formula <- as.formula(paste(factor, paste(traits, collapse=" + "), sep=" ~ "))
lda1cv <- lda(formula, data= model_data, CV = T)
#lda1cv <- lda(as.factor(FACTOR)~ SD_110DAP + TTFW + CR_90DAP, data=temp2, CV = T)
as1 <- sum(diag(prop.table(table(model_data[,factor], lda1cv$class))))
lda1train <- lda(formula, data=model_data, subset = intrain, CV = F)
as2 <- sum(diag(prop.table(table(test[,factor], predict(lda1train, model_data[-intrain, ])$class))))

```

# 2.1 Cross-Validation

K-fold cross validation taken to its extreme, with K equal to N, the number of data points in the set.

```{r, echo = FALSE}
as1
```

# 2.2 Percentage of correct predicted values

```{r, echo = FALSE}
as2
```


# 3. Plotting Linear Discriminant Analysis

```{r, echo = FALSE, fig.height = 10, fig.width = 12, warning=FALSE}
#datos <- na.omit(data)
myColors <- colors()[c(258, 144, 75)]
factor_levels <- levels(data[,factor])
#print(factor_levels)
model_data [, factor] <- factor(model_data[,factor], levels = factor_levels)

names(myColors) <- levels(model_data[,factor])
colScale <- scale_colour_manual(name = "Treat",values = myColors)
#Treatment contraction names must be the same used in Module 8.1 – Abiotic Stress protocol.

# 6.3. Generate a Train and Test data set
set.seed(1)
intrain <- sample(nrow(model_data), round(0.50*nrow(model_data)))
train <- model_data[intrain, ]
test <- model_data[-intrain, ]

library(gridExtra)
library(ggplot2)
# 6.4. Plotting the discrimination coefficients in a bi-dimensional graph. Note that what is written in red must be replaced for the respective selected traits
#lda2train <- lda(as.factor(TREAT)~ DSI_a + SD_Slp + ChCI_Slp + CR_Slp, data=dallpc, CV = F)
modelo <- as.formula(paste(factor, paste(traits, collapse=" + "), sep=" ~ "))
lda2train <- lda(modelo, data= model_data, CV = F)
prop.lda =  lda2train$svd^2/sum(lda2train$svd^2)
plda <- predict(object = lda2train, newdata = model_data )
dataset = data.frame(Factor_col = model_data[,factor], lda = plda$x)
p1.1 <- ggplot(dataset) + geom_point(aes(lda.LD1, lda.LD2, colour = Factor_col), size = 2) + xlim(-4, 4) + ylim(-5, 1) +
  labs(x = paste("LD1 (",  ")", sep=""),
       y = paste("LD2 (",  ")", sep="")) +
  #ggtitle('Linear Discriminant analysis\nTraits: DSI, SD_Slp, ChCI_Slp, CR_Slp') +
  ggtitle('Linear Discriminant analysis\nTraits: DSI, SD_Slp, ChISPAD_Slp, CR_Slp') +
  theme(plot.title = element_text(hjust = 0.5, size = 10))
grid.arrange(p1.1 + colScale)

```

